PANCHANGE_descriptives

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Added phq prepan retro scatterplots for participants reporting much better and a little better

#Correlation between whole sample retro impute and prepan
##Create function to use for all of the corplots

@@

```{r Whole sample scatterplots for gad and phq prepan retro}

@@

@@

```{r Little/much better scatterplots for gad}

@@

#Filter by participants reporting little/much better in gad since pandemic started (separetely and grouped)

little_better_gad_scatter <- dat %>% 
  filter(gad.pandemic_felt_feelings == "A little better")

much_better_gad_scatter <- dat %>% 
  filter(gad.pandemic_felt_feelings == "Much better")

much_little_better_gad_scatter <- dat %>% 
  filter(gad.pandemic_felt_feelings == "Much better" | 
           gad.pandemic_felt_feelings == "A little better")

@@

>>>>

#Correlations of retro impute and prepan
##Create function to use for all of the corplots

@@

```{r Whole sample prepan retro scatterplots prep}

@@

```{r Whole sample prepan retro scatterplots}

@@

```{r Little/much better prepan retro scatterplots prep}

@@

#Filter by participants reporting little/much better in gad and phq since pandemic started (separetely and grouped)

little_better_gad_scatter <- little_much_better_retro_prepan %>% 
  filter(gad.pandemic_felt_feelings == "A little better")

much_better_gad_scatter <- little_much_better_retro_prepan %>% 
  filter(gad.pandemic_felt_feelings == "Much better")

much_little_better_gad_scatter <- little_much_better_retro_prepan %>% 
  filter(gad.pandemic_felt_feelings == "Much better" | 
           gad.pandemic_felt_feelings == "A little better")

little_better_phq_scatter <- little_much_better_retro_prepan %>% 
  filter(phq.pandemic_felt_feelings == "A little better")

much_better_phq_scatter <- little_much_better_retro_prepan %>% 
  filter(phq.pandemic_felt_feelings == "Much better")

much_little_better_phq_scatter <- little_much_better_retro_prepan %>% 
  filter(phq.pandemic_felt_feelings == "Much better" | 
           phq.pandemic_felt_feelings == "A little better")

```{r Little/much better prepan retro scatterplots}

@@

little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little better",
                      sep=" "),
        subtitle = paste("n", dim(little_better_phq_scatter)[1]))

much_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better",
                      sep=" "),
        subtitle = paste("n", dim(much_better_phq_scatter)[1]))

much_little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") + 
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better and a little better",
                      sep=" "),
        subtitle = paste("n", dim(much_little_better_phq_scatter)[1]))
